Methods and Results

### 2022-10-06 ms.Rmd
Ronding data frame

  pacman::p_load(tidyverse, metafor, brms, orchaRd, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
eval(metafor:::.MuMIn)
```

@@

  table_fixed <- data.frame( Parameter = c("Intercept", "Treatment (Control)", "ln Mean", ""), 
                            Estimates = c(coefs_lnSD, ""),
                       `Upper 95% CI` = c(ci.ub_lnSD, ""),
                       `Lower 95% CI` = c(ci.lb_lnSD, ""), check.names = FALSE, row.names = NULL)

@@

  table_rand <- data.frame(     Parameter = c("Study", "Residual", "Species", "tau^2", "rho"), 
                                Estimates = dat$est, 
                           `Upper 95% CI` = dat$lb,
                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL)
```

@@

>>>>

  pacman::p_load(tidyverse, metafor, brms, orchaRd, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table, forestmangr)
eval(metafor:::.MuMIn)
```

@@

  table_fixed <- forestmangr::round_df(data.frame( Parameter = c("Intercept", "Treatment (Control)", "ln Mean", ""), 
                            Estimates = as.numeric(c(coefs_lnSD, "")),
                       `Upper 95% CI` = as.numeric(c(ci.ub_lnSD, "")),
                       `Lower 95% CI` = as.numeric(c(ci.lb_lnSD, "")), check.names = FALSE, row.names = NULL), digits = 3)

@@

  table_rand <- forestmangr::round_df(data.frame(     Parameter = c("Study", "Residual", "Species", "tau^2", "rho"), 
                                Estimates = dat$est, 
                           `Upper 95% CI` = dat$lb,
                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL), digits = 3)
```

@@

Overall, our results were largely consistent with our analysis using lnCVR, with average variability differences being estimated to be approximately similar (See Table S\@ref(tab:tables1)).
